Approximation as Differentiation

### 2025-06-09 main/first-order.tex
LatGal as a CMon-category.

The projections $\pi_1$ and $\pi_2$ from the product lattice $X \times Y$, have both upper and lower adjoints;
this means that $X \times Y$, which we shall hereafter write as $X \biprod Y$, is both a product and a
coproduct, with projections $\biproj_X$ and $\biproj_Y$ and injections $\biinj_X$ and $\biinj_Y$ given by:

>>>>

$\LatGal$ also has biproducts. The projections $\pi_1$ and $\pi_2$ from the product lattice $X \times Y$ have
both upper and lower adjoints; this means that $X \times Y$, which we shall hereafter write as $X \biprod Y$,
is both a product and a coproduct, with projections $\biproj_X$ and $\biproj_Y$ and injections $\biinj_X$ and
$\biinj_Y$ given by:
